### 2019-11-18 paper/results.tex
Results edits except #27

\section{Results and discussion} \label{Results-and-discussion}

\subsection{Thorium feed mechanism}

The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Nevertheless, 
the continuous feed flow of thorium and $^{233}$U helps to operate the 
\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

The non-thorium feed mechanism allows continuous feed flow of 
$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
is excluded from the non-thorium feed mechanism study.
The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the four fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the BOL. 
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}

For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because of the \glspl{MA}\footnote{In the present work, the minor actinides 
(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
fuel are less attractive for the non-thorium feed mechanism. The continuous LEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, reactor-grade Pu and TRU are the only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

@@

Figures~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC} demonstrate 
the evolution of important isotopes for the $^{233}$U, Pu, and TRU cases 
respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
$17.8$  $kg$ at the end of the operation time. 
Additionally, the mass of minor actinides (MA) and Pu increases with time. The level of Pu in the fuel salt correlates with the mass of the MA; however, MA need more time to reach equilibrium than Pu. Uranium inventory increases during 
operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with thorium helps 
maintain an almost constant inventory throughout the full operation time. 
For the Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the Pa extraction time was selected to be 30 s 
to avoid poisoning the core. Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryCCCC.png}
	\vspace{-0.4in}
	\caption{Evolution of the important nuclides inventories for the $^{233}$U 
		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
	\label{fig:inventoryCCCC}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
	\vspace{-0.5in}
	\caption{Evolution of the important nuclides inventories for the 
		reactor-grade Pu case (solid lines) and for the TRU case (dashed lines).}
	\label{fig:inventoryPu_TRUCCC}
\end{figure}

Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. The thorium inventory 
decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
feed mechanism is applied. 
In contrast, thorium total mass decreases significantly in the Pu and TRU cases when the non-thorium 
feed mechanism is applied. Thus, thorium mass decreases by $39.21$\% and 
$37.96$\% for the reactor-grade Pu and TRU cases, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Th232CC.png}
	\caption{The variation of thorium mass in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:Th232CC}
\end{figure}

@@

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
According to literature, the limit of Pu solubility in the FLiBe salt is 
$\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
(mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu fraction increases 
slightly but still below its solubility limit. On the other hand, the Pu 
fraction in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu fraction in the fuel salt (mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
In the $^{233}$U and reactor-grade Pu cases, the net production of 
$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. As shown in 
Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
$^{233}$U. In addition, Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative; 
about $175.28$ $kg$ of $^{233}$U must be added during this period. 
In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
proper feed mechanism and initial fissile material. 
Specifically, applying the non-thorium feed mechanism on 
the SD-TMSR loaded by reactor-grade Pu allows the 
transition to the thorium fuel cycle after $\approx$ 
$4.5$ years. Additionally, applying the thorium feed mechanism on 
the SD-TMSR loaded by $^{233}$U allows the 
transition to the thorium fuel cycle after $\approx$ $26$ years of operation. 
The comparison between the two feed mechanisms with different types of initial 
fuel is listed in Table~\ref{tab:comp_feeds}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{NetCC.png}
	\caption{Net production of $^{233}$U during the burnup period (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:NetCC}
\end{figure}

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled \gls{SD-TMSR}.
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

More changes in thermal neutron flux shape and magnitude for the 
$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
significant changes are observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

@@

In the first case, the fuel temperature change only impacts cross section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry change due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on the Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Six factor analysis}
The effective multiplication factor can be expressed as follows:
\begin{align}
k_{eff} &= \eta f p \epsilon P_f P_t
\intertext{where}
\eta     &= \mbox{thermal fission factor} \nonumber \\
f        &= \mbox{thermal utilization factor} \nonumber \\
p        &= \mbox{resonance escape probability} \nonumber \\
\epsilon &= \mbox{fast fission factor} \nonumber \\
P_f      &= \mbox{fast non-leakage probability} \nonumber \\
P_t      &= \mbox{thermal non-leakage probability.} \nonumber
\end{align}

@@

In contrast, the neutron reproduction factor ($\eta$), resonance escape 
probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
the initial and equilibrium state for all three initial fissile materials.  
$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
initial fissile materials provide a much harder neutron spectrum than 
$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
$p$ decreases during reactor operation. The thermal fission factor ($\eta$)  
increases during reactor operation for the $^{233}$U as initial fuel due to 
the accumulation of fissile plutonium isotopes, which produce more neutrons 
per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
evolution agrees with previously determined evolution parameters for a similar 
single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
rykhlevskii2019modeling, park_whole_2015}.

>>>>

\section{Results and discussion} \label{Results-and-discussion}
The molar fraction of the heavy metal (HM) 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL).
\subsection{Thorium feed mechanism}
The thorium feed mechanism continuously feeds thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}.
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
the SD-TMSR is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. For U-233 case, 
the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
\gls{SD-TMSR} for a 60 year lifetime (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

The non-thorium feed mechanism continuously feeds 
$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
is excluded from the non-thorium feed mechanism study.
Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
show promising results relative to the other two cases (HALEU and Pu+HALEU) (see Figure~\ref{fig:keff2}). 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
			\vspace{-0.5in}
	\caption{The change of the effective multiplication factor during 60 
	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
	interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}

For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs. 
For the \gls{TRU} fuel salt, the amount of 
$^{233}$U and the external feed flow of TRU is barely enough to operate the 
reactor for a long period of time ($\approx$ $40$ years) without any 
external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
because of the \glspl{MA}\footnote{In the present work, the minor actinides 
(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the HALEU and Pu+HALEU 
fuel are less attractive for the non-thorium feed mechanism. The continuous HALEU 
feed increases the amount of fertile $^{238}$U and consequently, reduces the 
feasibility of such fissile materials. According to the $k_{eff}$ 
results, reactor-grade Pu and TRU are the only alternative fissile materials that  
can be used to startup and maintain operation of the \gls{SD-TMSR}.

@@

Figures~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC} demonstrate 
the evolution of important isotopes for the $^{233}$U, Pu, and TRU cases 
respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
$17.8$  $kg$ at the end of the operation time. 
Additionally, the mass of minor actinides (MA) and Pu increases with time. The level of Pu in the fuel salt correlates with the mass of the MA; however, MA need more time to reach equilibrium than Pu. Uranium inventory increases during 
operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with thorium helps 
maintain an almost constant inventory throughout the full operation time. 
For the Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the Pa extraction time was selected to be 30 s 
to avoid poisoning the core. Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
elements for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryCCCC.png}
	\vspace{-0.4in}
	\caption{Evolution of important nuclide inventories for $^{233}$U 
		startup fuel (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
	\label{fig:inventoryCCCC}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
	\vspace{-0.5in}
	\caption{Evolution of important nuclide inventories for the 
		reactor-grade Pu case (solid lines) and for the TRU case (dashed lines).}
	\label{fig:inventoryPu_TRUCCC}
\end{figure}

Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. The thorium inventory 
decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
feed mechanism is applied. 
In contrast, thorium total mass decreases significantly in the Pu and TRU cases when the non-thorium 
feed mechanism is applied. Thus, thorium mass decreases by $39.21$\% and 
$37.96$\% for the reactor-grade Pu and TRU cases, respectively.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Th232CC.png}
	\caption{Mass variation of all thorium isotopes in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:Th232CC}
\end{figure}

@@

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
criticality, which increases the Pu mole concentration (\%) in the molten salt. 
The Pu solubility in FLiBe is 
$\approx$ $4.0$ \% \cite{ignatiev2012progress,sood1975plutonium}. 
Figure~\ref{fig:PusolubilityCC} represents the Pu mole concentration variation in the fuel salt 
for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu mole concentration increases 
slightly but still below its solubility limit. On the other hand, the Pu 
mole concentration in the molten salt loaded by TRU increases during operation and 
reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
be solved by increasing the reactor operation temperature or reducing the 
HM initial inventory \cite{zou2018transition}.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu mole concentration in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:PusolubilityCC}
\end{figure}
\FloatBarrier

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
zero. 
Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (see Figure~\ref{fig:keff2}).
In the $^{233}$U and reactor-grade Pu cases, the net production of 
$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
case the net production of $^{233}$U during the first 455 days is negative; 
about $175.28$ $kg$ of $^{233}$U must be added during this period. 
As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
$^{233}$U. 
To avoid the nuclear weapons proliferation, we recommended stopping the SD-TMSR after producing the required $^{233}$U ($\approx$ $4.5$) and replacing the core fuel by Th/$^{233}$U fuel.

In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
proper feed mechanism and initial fissile material. 
Specifically, applying the non-thorium feed mechanism on 
the SD-TMSR loaded by reactor-grade Pu allows the 
transition to the thorium fuel cycle after $\approx$ 
$4.5$ years. Additionally, applying the thorium feed mechanism on 
the SD-TMSR loaded by $^{233}$U allows the 
transition to the thorium fuel cycle after $\approx$ $26$ years of operation. 
The comparison between the two feed mechanisms with various initial fuel types 
is listed in Table~\ref{tab:comp_feeds}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{NetCC.png}
	\caption{Net production of $^{233}$U with burnup (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
	\label{fig:NetCC}
\end{figure}

@@

\subsection{Neutron spectrum}
Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
to the accumulation of Pu and other strong thermal neutron absorbers in the 
fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
similar to the initial thermal spectrum of a $^{233}$U fueled \gls{SD-TMSR}.
 \begin{figure}
 	\centering
 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
 			\vspace{-0.4in}
 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
 		fuel salt compositions (for all cases, the neutron flux
 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

@@

More changes in thermal neutron flux shape and magnitude for the 
$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
significant changes are observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}, thus, the core geometry (e.g., channels lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

@@

In the first case, the fuel temperature change only impacts cross section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry change due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on the Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature ($\alpha_{D,fuel}$) &$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density ($\alpha_{l,fuel}$) &$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel ($\alpha_{fuel})$ &$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature ($\alpha_{D,M}$) &$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core ($\alpha$) &$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Six factor analysis}
The effective multiplication factor can be expressed as follows:
\begin{align}
k_{eff} &= \eta f p \epsilon P_f P_t
\intertext{where}
\eta     &= \mbox{neutron reproduction factor} \nonumber \\
f        &= \mbox{thermal utilization factor} \nonumber \\
p        &= \mbox{resonance escape probability} \nonumber \\
\epsilon &= \mbox{fast fission factor} \nonumber \\
P_f      &= \mbox{fast non-leakage probability} \nonumber \\
P_t      &= \mbox{thermal non-leakage probability.} \nonumber
\end{align}

@@

In contrast, the neutron reproduction factor ($\eta$), resonance escape 
probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
the initial and equilibrium state for all three initial fissile materials.  
$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
initial fissile materials provide a much harder neutron spectrum than 
$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
$p$ decreases during reactor operation. The neutron reproduction factor ($\eta$)  
increases during reactor operation for the $^{233}$U as initial fuel due to 
the accumulation of fissile plutonium isotopes, which produce more neutrons 
per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
evolution agrees with previously determined evolution parameters for a similar 
single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
rykhlevskii2019modeling, park_whole_2015}.
